\section{Introduction}

Geographical authentication
is the task of certify that someone is at a certain place;
that is,
the task of authenticating someone's geographical location.
This problem has been considered for over 20 years~\cite{denning_1996}.
The authors of \cite{denning_1996} consider the problem of finding
the location of an intruder;
other applications include geographically restricted broadcasts~\cite{gdpr},
checkins at Foursquare,
and withdrawing cash at an ATM.

In all these examples,
there is a central authority which confers authentication services.
Besides all the traditional problems with centralized solutions,
like having a single point of failure,
services like Foursquare have to essentially believe the user's word
when attesting they were at a certain place~\cite{glas2015breaking}.
ATM's circumvent this by essentially being a large network of totems,
which is expensive~\cite{totem_patent}.

The above solutions suffer from either having to trust too heavily upon
the user's word, or from implementing an expensive network of totems to
vet user dishonesty. The former makes a system unreliable, while the latter
imposes a startup cost that is not realistic for small players trying to enter
the market.

For reasons of decentralization and low cost, we would like a
means of local geographic authentication where users---each user represented as
a smartphone---mutually and simultaneously encode their geographic location using
handshakes with nearby users. In this work, we show that there exists a
blockchain-like distributed ledger protocol which, when implemented on top of some
smartphone ad hoc network (SPAN), encodes user geotemporal information strictly in
terms of the topology of that user's local blockchain. We further present a simulation
package which---unlike any preexisting package know to the authors---allows for the
simulation of a blockchain-like ledger system implemented over arbitrary SPAN
topologies.

\section{Motivation}
\label{sec:motivation}

Many smartphones today are equipped with wireless functionality specifically
geared towards interacting with other smartphones in near geographic proximity.
Assuming these connections faithfully represent one's geographic
authentication\footnote{This is an important problem which we do not attempt to
address in this paper. We are only concerned with whether a blockchain-like distributed
ledger implemented over a SPAN can reliably encode information about the SPAN's evolution
over time using nothing more than the topology of local copies of the blockchain.},
it follows immediately that, if each smartphone is a node $u$ connected to node $v$ if and only
if $u$ and $v$ are within interaction proximity---the set of neighbors of $u$ serves as
a valid representation of $u$'s geographic location. Further, if two nodes $u,v$ claim to be
in the same geographic location (given the location is sufficiently granular), it is expected
that the set of neighbors they report would significantly overlap. For this reason,
recording ``handshakes'' with peers in geographic proximity should serve as a valid
representation of one's location over time.

\subsection{Three Evolving Topologies: Implications of Blockchain over a SPAN}

The Bitcoin protocol is heavily dependent on a few assumptions concerning
the topology of the underlying network. While it relies on the fact that no
node can have global knowledge of what nodes are in the network due to the
ease with which nodes may enter and exit the network, it also assumes that the
network is stable enough to offer such features as never partitioning and never
being susceptible to man-in-the-middle attacks~\cite{nakamoto2008bitcoin}. This
relative stability is what allows all nodes in the network to asymptotically
agree on which blocks constitute the global blockchain. Further, this global
blockchain naturally arises as the set-theoretic intersection of all local 
chains in the network.

Implementing a blockchain system over a SPAN, however, breaks all of the
aforementioned assumptions. SPANs are highly volatile, and they can easily
partition into disconnected components. This makes the idea of nodes
globally converging to agreement on what is a global blockchain ridiculous, as
the intersection of all local blockchains would cease to grow as soon as
nodes disagree on which is the longest chain. It is guaranteed, however,
that for all nodes $u$ in the SPAN $G$, there exists some neighborhood
$U\subset G$ containing $u$ such that, if one takes the intersection
$$\mathbf{B}_U=\bigcup_{u^\prime\in U}\mathcal{B}_{u^\prime}$$
of all local blockchains $\mathcal{B}_{u^\prime}$ for all $u^\prime\in U$, 
it holds that $\mathbf{B}_U$ grows nontrivially for all timesteps\footnote{To 
	see that this is correct, it is sufficient to note that this trivially
	holds for $U=\{u\}$.}.

The degree to which all subsets $U\subset G$ satisfy this property is the
degree to which a global blockchain is well defined, and the degree to which
most subsets $U$ fail to do so can serve as a measure of the degree to which
a global blockchain is poorly defined. For this reason, the authors present
the idea of a \textit{semi-global blockchain}: the global blockchain with regards
to a connected subnetwork $U$ of the network $G$, as arises
as the set-theoretic intersection of all local chains $\mathcal{B}_u$ held by
nodes $u\in U$.

\begin{figure*}
	\centering
	\begin{tabular}{|p{2cm}||p{5cm}|p{1.5cm}|p{2.5cm}|p{3cm}|}
		\hline
		\ & \textbf{P2P Topology} & \textbf{Local Block-chain (per node)} & \textbf{Global Blockchain} & \textbf{Semi-Global Blockchain (per neighborhood)}\\
		\hhline{|=||=|=|=|=|}
		\textbf{Bitcoin P2P} 
			& The Bitcoin protocol relies on the assumption that
				no node in the underlying network can have
				complete global knowledge of the state of the
				network, especially given nodes can spontaneously enter or
				exit the network. However, it is also assumed that
				this network never becomes disconnected and never
				becomes vulnerable to man-in-the-middle attacks.
				In this way, it is safe to assume that all local
				nodes can eventually agree on some global state
				information.
			& Very similar, up to slight differences in protocol
			& The global blockchain is implicitly induced as the
				set-theoretic intersection of all local blockchains.
				It is guaranteed in probability that this intersection
				chain is always growing; failure to grow would imply
				that this global chain has forked.
			& For any connected subnetwork $G^\prime$ of the network, the
				global chain of the restriction to $G^\prime$ always
				(asymptotically) agrees with the well-defined global
				chain. \\
		\hline
		\textbf{SPAN P2P}
			& SPANs are highly volatile. The frequent making and
				breaking of connections causes the SPAN
				to fragment into disconnected components. It is hopeless,
				therefore, to assume that all the nodes will ever
				agree on global state information that is not
				granted \textit{a priori}.
			& Very similar, up to slight differences in protocol
			& Though the set-theoretic intersection of all local
				blockchains is well-defined, this intersection is
				likely to be noninteresting and stop growing after some
				timestep due to forking.
			& Let $G$ be the network. For each node $u\in G$, there exists
				neighborhoods $U,u\in U\subset G$ such that the global
				chain is well defined with respect to the restriction
				to $U$. We can define \textit{semi-global blockchains}
				as the intersection of local chains with respect to
				such restrictions. \\
		\hline
	\end{tabular}
	\caption{The Nakamoto paper assumes that the blockchain protocol is
		implemented over a relatively stable P2P network. If we attempt to
		implement a blockchain protocol over a SPAN, however, many of the
		notions that naturally arise in the case of Bitcoin no longer appear.
		The SPANchain simulator was written to allow for easy simulation of 
		blockchains implemented over SPANs, together with graphic tools which
		the authors hope helps the research community come up with ways
		of studying semi-global blockchains in the case of a forking global chain.}
	\label{tab:three_table}
\end{figure*}

Traditionally,
blockchain networks strive mantain a single longest path
starting from the root of the chain;
that is,
the goal is to avoid global forks.
In the case of Bitcoin,
for example,
local, temporary forking still happens
but one of those forks is usually quickly abandoned by the network~\cite{decker_2013}.
In our case,
since SPANs are often disconnected,
the global blockchain will eventually fork.
We actually embrace forking as a feature:
each long-term fork represents a connected component of the underlying SPAN.

\section{The SPANchain Simulator}
\label{sec:SPANchain}

We present a tool which allows for the simulation of the evolution of SPANs
---represented as random geometric graphs---over time, and which, most saliently,
allows for the simulation of a novel blockchain-like distributed ledger overlaid
on this SPAN. While the authors are aware of 1) network simulation tools that
accommodate dynamic network topologies~\cite{chaudhary2012study} and
2) tools for simulating blockchain
systems distributed over a network of nodes, we are unaware of any tool that
allows for the simulation of a blockchain system implemented over arbitrary dynamic
networks. Part of the reason for this is that SPANs, by nature, induce a network topology
that fragments easily and from which nodes enter and exit with great frequency. For
conventional blockchain systems, this inevitably leads to forking in the global
chain---a property which, for cryptocurrency applications, is highly undesirable
~\cite{decker_2013,nakamoto2008bitcoin}. Using our simulation tool, however, we show
that the way global forks form in blockchain networks implemented over SPANs can encode
geotemporal information about how the SPAN evolves over time.

In order to observe the behavior of this network under several scenarios,
we wrote a simulator package SPANchain%
\footnote{
	The code for the simulator is publicly available at
	\url{https://github.com/robbobbinett/geographic_auth_with_bc}.
}
for the protocol.

To the best of our knowledge,
this is the first blockchain simulation framework which simulates
blockchains implemented over SPANs, as well as the first
to embrace forking as a feature rather than a bug.
Therefore,
there are no packages which are capable of simulating a forking blockchain.
We also are not aware of any packages that implement blockchains over SPANs.

Although we implemented the protocol described in sections
\ref{sec:blockchain} in the simulator,
the package is written to be agnostic to the protocol for block formation,
as well as processes by which the underlying topology evolves\footnote{We have,
	however, implemented a class of SPAN-nodes to specifically handle
	the evolution of the SPAN with respect to a random geometric graph model.}.
We hope that these packages can be used by other researchers
to better understand how blockchains fork, and what information this forking
encodes with respect to the history of the underlying topology.
